The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-25 paper/ms.tex
more editting in the conclusions

As first we see how the width of the line changes using a modified FWHM
explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
rotation increase also the width increase in a factor of $2-3$ in comparison 
with the static case.

>>>>

Our main result is that rotation clearly impacte the \ly line
morphology. Double peaked lines can make transitions into single
peaked lines as the rotational velocity increases, off-centered
can result into triple peaked lines.

We have quantified the results in different aspects. In Section
\ref{sec:widthpeak} we show that the line width increases up to a
factor of $2-3$ in comparison to the static case. Simultaneously, the
flux in the line center also increases with rotational velocity. This
increase induces the transition form a double peak to a single peak
line in the models where the radiation sources are homogeneusly
distributed.

In the case of homogeneously distributed sources, the changes in
line morphology are linked to the reduction in the average number of
scatterings. In the second part of Section \ref{sec:widthpeak} we show
that, as rotational velocity increases, a large fraction of photons
escape with less than $10$ scatterings. This makes highly improbable
that a photon's frequency can move away from the line's center.

In contrast, for centrally located sources, the number of scatterings
does not significantly decrease. However, due to the increasing
bulk velocity of the gas, each scattering is inefficient in shifting
photons away from the line's center.

The changes in the number of scattering has a direct bearing on the
escape fraction. In Section \ref{}
